Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-21 article.rnw
Change the fig:aic label to fig:ic.
To reflect that it may use other information criteria.
Correct "AIC weights" to "Akaike weights".
This will be especially if they are calculated from AICc instead of AIC.

The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.
The AIC values ranged from \icnum{\Sexpr{min(brute_data$statistics[[ic]])}} to \icnum{\Sexpr{max(brute_data$statistics[[ic]])}}.
The ungrouped model gave an AIC value of \icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}.
\Cref{fig:aic} shows the distribution of AIC values from the models, with some models of interest marked.

@@

	\caption{%
		A histogram of the AIC values of species interaction models with all possible groupings of interaction coefficients.
		The green line shows the AIC value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model, in which all competition coefficients are fitted independently.
		The red line shows the AIC value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model, where every pair of species shares a single interaction coefficient.
	}
	\label{fig:aic}
\end{figure}

@@

	\caption{%
		Coclassification matrices of the Lotka--Volterra competitive effects and responses of the six studied \emph{Drosophila} species, weighted by AIC weights.
		The cell for a pair of species represents the probability that the best grouping, as determined by the AIC weights of the grouped models, places those two species in the same group.
		\Cref{fig:coclassification-cols} represents the grouping of species' competitive effects upon other species (columns of the interaction matrix), while \cref{fig:coclassification-rows} represents the grouping of species' responses to competition (rows of the interaction matrix).
	}
	\label{fig:coclassification}
\end{figure}

>>>>

The $R^2$ values of the models ranged from \rsquarednum{\Sexpr{min(brute_data$statistics$R2)}} to \rsquarednum{\Sexpr{max(brute_data$statistics$R2)}}.
The AIC values ranged from \icnum{\Sexpr{min(brute_data$statistics[[ic]])}} to \icnum{\Sexpr{max(brute_data$statistics[[ic]])}}.
The ungrouped model gave an AIC value of \icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}.
\Cref{fig:ic} shows the distribution of AIC values from the models, with some models of interest marked.

@@

	\caption{%
		A histogram of the AIC values of species interaction models with all possible groupings of interaction coefficients.
		The green line shows the AIC value (\icnum{\Sexpr{brute_data$fully_separated_statistics[[ic]]}}) of the ungrouped model, in which all competition coefficients are fitted independently.
		The red line shows the AIC value (\icnum{\Sexpr{brute_data$fully_grouped_statistics[[ic]]}}) of the fully grouped model, where every pair of species shares a single interaction coefficient.
	}
	\label{fig:ic}
\end{figure}

@@

	\caption{%
		Coclassification matrices of the Lotka--Volterra competitive effects and responses of the six studied \emph{Drosophila} species, weighted by Akaike weights.
		The cell for a pair of species represents the probability that the best grouping, as determined by the Akaike weights of the grouped models, places those two species in the same group.
		\Cref{fig:coclassification-cols} represents the grouping of species' competitive effects upon other species (columns of the interaction matrix), while \cref{fig:coclassification-rows} represents the grouping of species' responses to competition (rows of the interaction matrix).
	}
	\label{fig:coclassification}
\end{figure}
